The effect of climate forcing on numerical simulations of the Cordilleran ice sheet at the Last Glacial Maximum

### 2014-03-31 cordillera-climate.tex
Tabs to spaces
Add formatted references
Adapt article text to lapse-rate corrected figures

% Recognize utf-8 special characters
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% Set figures repository
\graphicspath{{figures/}}

@@

As previously outlined, significant differences in the distribution of winter (DJF) precipitation and summer (JJA) temperature, which are the predominant controls on accumulation and melt at the modelled ice sheet surface, exist between datasets (Figs.~\ref{fig:topo}--\ref{fig:prec}). In this section we use the WorldClim climatology, which is derived from observations, as a~reference with which to compare other climate forcing data on land. ERA-Interim, CFSR and NARR climatologies exhibit temperature distributions fairly consistent with WorldClim data (Fig.~\ref{fig:tempheatmap}). When examining the spatial distribution of temperature differences between reanalyses and WorldClim data, it appears that most of the disparity between reanalyses and observation data is caused by topographical detail at scales unresolved in the reanalysis datasets (Fig.~\ref{fig:tempdiff}). Surface air temperature data from the NCEP/NCAR climatology shows the largest disparity with that of WorldClim, with a~significant cold anomaly over most of the modelling domain (Figs.~\ref{fig:tempheatmap} and \ref{fig:tempdiff}).

@@

% References
\bibliographystyle{copernicus}
\bibliography{references}

% ----------------------------------------------------------------------
% Floats
% ----------------------------------------------------------------------
\newpage

@@

% fig:tempheatmap
\begin{figure}
	\includegraphics{cordillera-climate-tempheatmap}
	\caption{Density maps showing a~comparison of summer (JJA) surface air temperature data from the WorldClim climatology, against that of each reanalysis. Apparent horizontal lines are an artefact of different horizontal resolutions. Colour mapping is based on a~logarythmic scale. Note the cold bias of NCEP/NCAR data relative to WorldClim data.}
	\label{fig:tempheatmap}
\end{figure}

% fig:tempdiff
\begin{figure}
	\includegraphics{cordillera-climate-tempdiff}
	\caption{Summer (JJA) surface air temperature difference maps against WorldClim data, after bi-linear spatial interpolation. Note the cold bias of NCEP/NCAR data and temperature anomalies due to unresolved topographic detail.}
	\label{fig:tempdiff}
\end{figure}

% fig:precheatmap
\begin{figure}
	\includegraphics{cordillera-climate-precheatmap}
	\caption{Density maps showing a~comparison of winter (DJF) precipitation rate from the WorldClim climatology, against that of each reanalysis. Apparent horizontal lines are an artefact of different horizontal resolutions. Apparent vertical lines at low values are an artefact of the low precision of WorldClim data. Colour mapping is based on a~logarythmic scale. Note the wet bias of all reanalysis data relative to WorldClim data.}
	\label{fig:precheatmap}
\end{figure}

>>>>

% Encoding
\usepackage[T1]{fontenc}

% Figure directory
\graphicspath{{figures/}}

@@

As previously outlined, significant differences in the distribution of winter (DJF) precipitation and summer (JJA) temperature, which are the predominant controls on accumulation and melt at the modelled ice sheet surface, exist between datasets (Figs.~\ref{fig:topo}--\ref{fig:prec}). In this section we use the WorldClim climatology, which is derived from observations, as a~reference with which to compare other climate forcing data on land.

Because most of the disparity between reanalytic and observational temperature data is caused by topographical detail at scales unresolved in the reanalysis datasets, we apply a lapse-rate correction prior to this comparison, using the same lapse rate of 6\,\unit{{\degree}C\,km^{-1}} as in the simulations. ERA-Interim, CFSR and NARR climatologies exhibit temperature distributions fairly consistent with WorldClim data (Fig.~\ref{fig:tempheatmap}). The spatial distribution of temperature differences between reanalyses and WorldClim data shows partly consistent patterns, which may relate to weaknesses of WorldClim data in areas of sparse observational coverage (Fig.~\ref{fig:tempdiff}). However significant disparity among reanalyses exists, too. More specifically, surface air temperature data from the NCEP/NCAR climatology shows the largest disparity with that of WorldClim, with a~significant cold anomaly over most of the modelling domain (Figs.~\ref{fig:tempheatmap} and \ref{fig:tempdiff}).

@@

% References
\input{references.bbl}
\newpage

% ----------------------------------------------------------------------
% Floats
% ----------------------------------------------------------------------

@@

% fig:tempheatmap
\begin{figure}
  \includegraphics{cordillera-climate-tempheatmap}
  \caption{Density maps showing a~comparison of summer (JJA) surface air temperature data from the WorldClim climatology, against that of each reanalysis. Climate data are presented after bilinear spatial interpolation and correction for topographic differences to WorldClim data, using a lapse rate of 6\,\unit{{\degree}C\,km^{-1}}. Colour mapping is based on a~logarythmic scale. Note the cold bias of NCEP/NCAR data relative to WorldClim data.}
  \label{fig:tempheatmap}
\end{figure}

% fig:tempdiff
\begin{figure}
  \includegraphics{cordillera-climate-tempdiff}
  \caption{Summer (JJA) surface air temperature difference maps against WorldClim data, after bi-linear spatial interpolation and lapse-rate correction. Note the cold bias of NCEP/NCAR data and temperature anomalies due to unresolved topographic detail.}
  \label{fig:tempdiff}
\end{figure}

% fig:precheatmap
\begin{figure}
  \includegraphics{cordillera-climate-precheatmap}
  \caption{Density maps showing a~comparison of winter (DJF) precipitation rate from the WorldClim climatology, against that of each reanalysis, after bi-linear spatial interpolation. Colour mapping is based on a~logarythmic scale. Note the wet bias of all reanalysis data relative to WorldClim data.}
  \label{fig:precheatmap}
\end{figure}
